% ------------
% Cover Letter
% ------------
\section{Cover Letter}

\opening{COMPANY}

\letterparagraph{
  My name is Spencer C. Imbleau and I am applying for the position of
  \href{https://jobs.apple.com/en-us/details/200307364}{\myuline{GPU Kernel Mode Driver / Firmware Engineer (200307364)}}.
  I am in Orlando but serving as a Software Engineer for NASA at Kennedy Space Center!
}
\letterparagraph{
  I am dedicated and passionate when it comes to GPU architecture. I invite you
  to review my \href{http://dx.doi.org/10.13140/RG.2.2.25593.54887}{\myuline{published and defended theses}} on how to innovate and measure new
  imaging models on GPUs using current technology, as an example.
  I have written a \href{https://github.com/simbleau/simbleau/tree/research/capstone-bachelor}{\myuline{software rendered}} and \href{https://github.com/simbleau/power}{\myuline{hardware-accelerated}}
  game engines from scratch and continue to operate to look into imaging as a hobbyist allure. Most
  of my open-source contribution lands its way in the ecosystem of Rust and Bevy for now, but
  I have been working with (on a volunteer basis) graphics engineers from Mozilla and Google
  for years due to my research interests. I am confident I can be an asset to Apple's rich culture
  and principles. I am very proud of our commitments and impact worldwide, which is why I want to join Apple.
}
\letterparagraph{
  Regardless of research and open source works, my professional experience is in systems engineering for a Fortune 1000,
  software engineering at NASA, and leading research assistantships on vector image modelling studies.
  I believe I am someone who enjoys solving difficult problems, and that I would be a perfect fit given my obvious passion.
}
\letterparagraph{
  I've blessed this cover letter with a dogcow. Moof!

  Thank you for your time and consideration for this position!
}

\closing